Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-08-12 paper.tex
Addressing H2 Pop III criterion question

	\item molecular hydrogen fraction, f$_{\rm H2}$ > 10$^{-3}$
\end{enumerate}
%
\textbf{Our chosen threshold density corresponds to a value similar to a density that would trigger another mesh refinement past level 12.  At these scales, Jeans length refinement is the most common because of the cold temperatures in the cloud core.}

>>>>

	\item molecular hydrogen \textbf{number} fraction, f$_{\rm H2}$ > 10$^{-3}$
\end{enumerate}
\textbf{Our chosen threshold density are consistent with values found in previous simulations of Pop III star formation \citep[e.g.][]{Hirano15} at our resolution limit.  Additionally, it is similar to a density that would trigger another mesh refinement past level 12.  At these scales, Jeans length refinement is the most common because of the cold temperatures in the cloud core.  The molecular hydrogen criterion is also consistent with previous work in the ``loitering'' phase of molecule formation between $10^2$ and $10^8 \cubecm$ before three-body reactions become important \citep[e.g.][]{Omukai10}.}

### 2019-08-12 referee.tex
Addressing H2 Pop III criterion question

Our choice was motivated by our refinement strategy rather than convergence. We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12 (dx = 0.09 proper pc at $z=10$).  At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.  Solving for the density in the Jeans length equation, given a typical temperature $T=300$~K with primordial cooling and a Jeans Length of $8 \times \textrm{dx}$, we obtain a number density $n = 5.7 \times 10^4 \cubecm$.  This number density does not exactly match the chosen density criterion because some oversight when setting up the simulation.  In the case where the density SF criterion is larger than $n$, the gas will continue to condense on a faster timescale than its surroundings.  Thus we are confident that this slight mismatch does not affect our results.

@@

>>>>

Our choice was motivated by both previous work and our refinement strategy rather than convergence. Previous work (e.g. O'Shea et al. 2007; Yoshida et al. 2007) and later groups (e.g. Hirano et al. 2015) have shown that the number density is $\sim 10^6 \cubecm$ at our resolution limit of $0.09$ proper pc at $z=10$.  Secondly, we chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12 (dx = 0.09 proper pc at $z=10$).  At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.  Solving for the density in the Jeans length equation, given a typical temperature $T=300$~K with primordial cooling and a Jeans Length of $8 \times \textrm{dx}$, we obtain a number density $n = 5.7 \times 10^4 \cubecm$.  This number density does not exactly match the chosen density criterion because some oversight when setting up the simulation.  In the case where the density SF criterion is larger than $n$, the gas will continue to condense on a faster timescale than its surroundings.  Thus we are confident that this slight mismatch does not affect our results.

@@

We chose this critical H$_2$ fraction to match with the values found in previous work (e.g. Yoshida et al. 2007; Omukai et al. 2010) at the density threshold of $10^6 \cubecm$.  It is a number fraction.  We have added a note in Section 2.2.1 to reflect this detail.

In our original formulation (Abel et al. 2007), we implemented this restriction to avoid spurious star particle formation in D-type ionization fronts that can meet all of the other criteria.  But in the presence of an extremely strong Lyman-Werner flux from a nearby ($\sim$1 pc) star, star formation is unlikely to occur in the shell because it is irradiated and not self-gravitating. The last question is an interesting question, but it is difficult to determine because these conditions (high density but low H$_2$ fractions) are short-lived just after star formation.  Thus we cannot give a definite answer to it, but from the original formulation, we would estimate that the number of Pop III stars would increase by a factor of several with multiple cells in the quasi-spherical ionization front triggering star particle formation.  Because of these uncertainties, we have not added any of these details to the manuscript.
